---
title: "hw2"
author: "HanSun, HanSun97"
date: "2020.2.7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Rcommands
### Question 1
```{r}
celsius <- function(fahrenheit){
  cel <- ((fahrenheit-32)*(5/9))
  print(cel)
}
celsius(24)
celsius(15)
```

### Question 2
```{r}
vec200 <- 0
for (i in 1:200){
  if ((i%%2)==0)
    vec200[i] <- 1
  else
    vec200[i] <- 3
}
vec200
```

### Question 3
```{r}
numPerfect <- 0
for (i in 1:2001) {
  num <- 1
  while ((num*num) <= i) {
    if ((num*num) == i)
      numPerfect = numPerfect + 1
    num = num + 1
  }
  i = i + 1
}
print(numPerfect)
```

## Cars and mileage
```{r}
library(ggplot2)
head(mpg)
```

### Question 1
```{r}
sort(mpg$hwy,decreasing = TRUE)[1:3]
top3 <- mpg[mpg$hwy == 44|mpg$hwy == 41,]
top3

```

### Quesiton 2
```{r}
Compact <- mpg[mpg$class == 'compact',]
numCompact <- nrow(Compact)
numCompact
```

### Question 3
```{r}
plot(mpg$hwy,mpg$cty)
```

In this case, there are multiple points on the scatterplot having the same coordinates. Some of the these points overlap each other.

### Question 4
```{r}
mpg2008 <- mpg[mpg$year == 2008,]
mpg1999 <- mpg[mpg$year == 1999,]
par(mfrow = c(2,2))
hist(mpg2008$cty, main = "histogram of cty(2008)")
hist(mpg2008$hwy, main = "histogram of hwy(2008)")
hist(mpg1999$cty, main = "histogram of cty(1999)")
hist(mpg1999$hwy, main = "histogram of hwy(1999)")
par(mfrow = c(1,1))
plot(mpg2008$cty,mpg2008$hwy,col='red',xlab = 'cty',ylab = 'hwy')
points(mpg1999$cty,mpg1999$hwy,col='green')

```

In the highway, it shows if the car is more efficient in a high speed. In the city, it shows if the the car is more efficient in a low speed. There are more cars in 15-30 hwy in 1999 and more cars in 10-20 cty in 1999, which means, the cars are more fuel efficient in 1999.